Assessing Amazon Turker and automated machine forecasts in the Hybrid Forecasting Competition

### 2019-01-04 slides/index.Rmd
fix redundant transition
update slides

---
title: Assessing Amazon Turker and automated machine forecasts in the Hybrid Forecasting Competition
author: "Predictive Heuristics </br>Andreas Beger and Michael D. Ward"
date: "`r format(Sys.Date(), '%e %B %Y')` </br>Asian POLMETH 2019, Kyoto, Japan"
output: 
  xaringan::moon_reader:
    css: ["default-fonts", "default", "custom_theme.css"]
    chakra: libs/remark-latest.min.js
    nature:
      beforeInit: "macros.js"
---

@@

@@

- Negative values $\rightarrow$ human forecasters did better

- Positive values $\rightarrow$ machine forecasts did better

>>>>

---
title: Assessing Amazon Turker and automated machine forecasts in the Hybrid Forecasting Competition
author: "Predictive Heuristics </br>Andreas Beger and Michael D. Ward"
date: "`r format(Sys.Date(), '%e %B %Y')` </br>Asia POLMETH 2019, Kyoto, Japan"
output: 
  xaringan::moon_reader:
    css: ["default-fonts", "default", "custom_theme.css"]
    chakra: libs/remark-latest.min.js
    nature:
      beforeInit: "macros.js"
---

@@

# Performance by forecaster group

|Forecaster | avg Brier|     N|
|:----------|---------:|-----:|
|Machine    |     0.402|  1975|
|Turker     |     0.433| 39140|
|Volunteer  |     0.322|  7816|

@@

- Negative values $\rightarrow$ human forecasters did better
- Positive values $\rightarrow$ machine forecasts did better
